Visualizations for the manuscript

### 2022-04-06 metanalysis_visualization/manuscript_Figures.Rmd
updating results

```{r}
outputDir <- "../../output/previous_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = "../public-data/country_mapping.txt")
```

@@

```{r Interrupted time series by sex}
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))

@@

ggplot(bootstrapped_fitted_disorder,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total,
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
# ggsave("boostrapped_disorders.png", height = 20, width = 45, units = "cm")

>>>>

```{r}
outputDir <- "../../output/latest_output//"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = "../public-data/country_mapping.txt")
```

@@

```{r }
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))

@@

ggplot(bootstrapped_fitted_disorder,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total,
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_disorders.png", height = 14, width = 25, units = "cm")
